### 2013-09-24 evaluation/paper.tex
compute feature numbers for all models ^^

This means the unary potential has $16 \cdot 8 \cdot 26$ parameters, one for each input

@@

\subsection{Multi-Label Classification}
Multi-label classification is a generalization of multi-class classification,
in which each example can be associated with more than one class. In other
words, the algorihm must decide for each sample and for each class whether the
sample belongs to that class or not.
Multi-label classification was first formulated as a structured prediction problem
in by \citet{finley2008training}, where it was used to investigate the influence of
approximate inference on the $n$-slack cutting plane algorithm. In this formulation,
each class is represented as a binary node in a factor graph---the states representing
presence of absence of the class. A different factor of pairwise potentials is introduced
between each pair of classes.
We also consider a different model, where pairwise potentials are only
introduced between specific nodes. Build a tree over the binary variables by
computing the Chow-Liu Tree~\citep{chow1968approximating} of the targets. While
this results in a less expressive model, a tree-shaped model allows for exact
inference via message passing.
We use two of the datasets used in \citet{finley2008training}, the scene
and yeast datasets. We choose these two as these are real-world datasets for
which the pairwise approach outlined above actually improves upon the
baseline~\citep{finley2008training}.
The scene dataset has six labels, 294 input features, 1211 training samples and
1196 test samples. This leads to $204 \cdot 6$ parameters for the unary potentials,
$3 \cdot 5 \cdot 4$ parameters for the full pairwise potentials (four for each edge), and
$5 \cdot 4$ parameters for the pairwise potentials of the tree-shaped model.
Using four parameters for each edge is a slight over-parametrization that
simplifies writing out the model.
The yeast dataset has 14 labels, 103 features, 1500 training samples and 971
test samples. The resulting numbers of parameters are $14 \cdot 103$ parameters
for the unary potentials, $7 \cdot 13 \cdot 4$ parameters for the full pairwise
potential, and $13 \cdot 4$ parameters for the tree-shaped model.

@@

We use a grid CRF model for this task. Unary for each node are given by the
input of the 8-neighborhood of the node---using a 4-neighborhood would most
likely yield better results, but we do not want to encode too much
task-knowledge into our model.
Using the one-hot encoding of the input, this leads to $9 \dot 5 = 45$ unary features.
With 11 output classes, the unary potential has $11 \cdot 9 \cdot 5$ parameters.
Features for the pairwise potentials are constructed by concatenating the features
of the two neighboring nodes, taking the direction of the edge into account.
The pairwise feature therefore has dimensionality $45 \cdot 4$, with the first
$45$ entries corresponding to the feature of the ``top'' node, the second $45$
entries to the features ``bottom'' node, followed bye the ``left'' and
``right'' nodes. As each edge is either horizontal \emph{or} vertical, only two
of these parts will be non-zero for any given edge.  With $45 \cdot 4$ edge
features, the pairwise potentials has $45 \cdot 4 \cdot 11^2$ parameters.

\subsection{Superpixel CRFs for Semantic Segmentation}
Our main attention is devoted to the use of conditional random fields for
semantic segmentation.  We use the Pascal VOC and MSRC datasets. A detailed
description of the method will be given in Chapter~\ref{ch:exact_learning}.
%TODO will it?
The Pascal VOC has \ldots training and \ldots test images, each having
around 100 superpixels. There are 20 object categories, plus background. The % TODO check!
MSRC dataset has \ldots training and \ldots test images, also segmented in
around 100 superpixels each. We use the MSRC-21 dataset, which has 21 target
classes.
Each superpixel is represented as an output variable, with the ground truth obtained
by majority vote over the pixel belonging to the superpixel.
Pairwise potentials were introduced for each pair of neighboring superpixels.
We then removed all superpixels that were labeled as ``void'', together with
their pairwise potentials.
As unary potentials, we use the TextonBoost probabilities provided by \citet{krahenbuhl2012efficient}.
We average probabilities inside each superpixel, yielding 21 input features for both datasets.
We also used the same pairwise features for the two datasets: a constant feature,
a color contrast feature, and a feature encoding relative vertical position between superpixels.
Overall, the models for both datasets had $21 \cdot 21 + 21^2 \cdot 4$ features.
It is possible to assume symmetric potentials for this dataset, leading to less
pairwise features. We found both parametrizations yielded similar results.

\begin{table}
    \caption{Summary of Datasets.\tablabel{datasets}}
    \begin{tabu} to \linewidth{@{}XXXXXX@{}}
    %\multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\
    \toprule
    Dataset    & samples & nodes & edges & dim w & labels\\
    \cmidrule{1-6}
    MNIST      & 60000   & 1     & none  &       & 10\\
    OCR-small  & 704     & 3--14 & chain &       & 26\\
    OCR-large  & 6173    & 3--14 & chain &       & 26\\
    scene-tree & 1211    & 6     & tree  &       & 2\\
    scene-full & 1211    & 6     & loopy &       & 2\\
    yeast-tree & 1500    & 14    & tree  &       & 2\\
    yeast-full & 1500    & 14    & loopy &       & 2\\
    snake      & 200     &84--168& loopy &       & 11\\
    MSRC21     & 276     & 7--113& loopy &       & 21\\
    Pascal VOC & 964     & 8--112& loopy &       & 21\\
    \bottomrule

>>>>

This means the unary potential has $16 \cdot 8 \cdot 26 = 768$ parameters, one for each input

@@

\subsection{Multi-Label Classification}
Multi-label classification is a generalization of multi-class classification,
in which each example can be associated with more than one class. In other
words, the algorihm must decide for each sample and for each class whether the
sample belongs to that class or not.
Multi-label classification was first formulated as a structured prediction problem
in by \citet{finley2008training}, where it was used to investigate the influence of
approximate inference on the $n$-slack cutting plane algorithm. In this formulation,
each class is represented as a binary node in a factor graph---the states representing
presence of absence of the class. A different factor of pairwise potentials is introduced
between each pair of classes.
We also consider a different model, where pairwise potentials are only
introduced between specific nodes. Build a tree over the binary variables by
computing the Chow-Liu Tree~\citep{chow1968approximating} of the targets. While
this results in a less expressive model, a tree-shaped model allows for exact
inference via message passing.
We use two of the datasets used in \citet{finley2008training}, the scene
and yeast datasets. We choose these two as these are real-world datasets for
which the pairwise approach outlined above actually improves upon the
baseline~\citep{finley2008training}.
The scene dataset has six labels, 294 input features, 1211 training samples and
1196 test samples. This leads to $204 \cdot 6 = 1224$ parameters for the unary potentials,
$3 \cdot 5 \cdot 4 = 60$ parameters for the full pairwise potentials (four for each edge), and
$5 \cdot 4 = 20$ parameters for the pairwise potentials of the tree-shaped model.
Using four parameters for each edge is a slight over-parametrization that
simplifies writing out the model.
The yeast dataset has 14 labels, 103 features, 1500 training samples and 971
test samples. The resulting numbers of parameters are $14 \cdot 103=1442$ parameters
for the unary potentials, $7 \cdot 13 \cdot 4=364$ parameters for the full pairwise
potential, and $13 \cdot 4=52$ parameters for the tree-shaped model.

@@

We use a grid CRF model for this task. Unary for each node are given by the
input of the 8-neighborhood of the node---using a 4-neighborhood would most
likely yield better results, but we do not want to encode too much
task-knowledge into our model.
Using the one-hot encoding of the input, this leads to $9 \dot 5 = 45$ unary features.
With 11 output classes, the unary potential has $11 \cdot 9 \cdot 5=495$ parameters.
Features for the pairwise potentials are constructed by concatenating the features
of the two neighboring nodes, taking the direction of the edge into account.
The pairwise feature therefore has dimensionality $45 \cdot 4$, with the first
$45$ entries corresponding to the feature of the ``top'' node, the second $45$
entries to the features ``bottom'' node, followed bye the ``left'' and
``right'' nodes. As each edge is either horizontal \emph{or} vertical, only two
of these parts will be non-zero for any given edge.  With $45 \cdot 4$ edge
features, the pairwise potentials have $45 \cdot 4 \cdot 11^2 =21780$ parameters.

\subsection{Superpixel CRFs for Semantic Segmentation}
Our main attention is devoted to the use of conditional random fields for
semantic segmentation.  We use the Pascal VOC and MSRC datasets. A detailed
description of the method will be given in Chapter~\ref{ch:exact_learning}.
%TODO will it?
The Pascal VOC has \ldots training and \ldots validation images, each having
around 100 superpixels. There are 20 object categories, plus background. The % TODO check! refer to other part
MSRC dataset has \ldots training and \ldots test images, also segmented in
around 100 superpixels each. We use the MSRC-21 dataset, which has 21 target
classes.
Each superpixel is represented as an output variable, with the ground truth obtained
by majority vote over the pixel belonging to the superpixel. We removed all
superpixels which were mostly ``void'', leading to some samples haven much
fewer than 100 variables.
Pairwise potentials were introduced for each pair of neighboring superpixels.
We then removed all superpixels that were labeled as ``void'', together with
their pairwise potentials.
As unary potentials, we use the TextonBoost probabilities provided by  % FIXME this !!
\citet{krahenbuhl2012efficient}.  We average probabilities inside each
superpixel, yielding 21 input features for both datasets.  We also used the
same pairwise features for the two datasets: a constant feature, a color
contrast feature, and a feature encoding relative vertical position between
superpixels.  Overall, the models for both datasets had $21 \cdot 21 + 21^2
\cdot 4$ features.  It is possible to assume symmetric potentials for this
dataset, leading to less pairwise features. We found both parametrizations
yielded similar results.

\begin{table}
    \caption{Summary of Datasets.\tablabel{datasets}}
    \begin{tabu} to \linewidth{@{}XXXXXX@{}}
    %\multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\
    \toprule
    Dataset    & samples & nodes & edges & dim w & labels\\
    \cmidrule{1-6}
    MNIST      & 60000   & 1     & none  & 7840  & 10\\
    OCR-small  & 704     & 3--14 & chain & 1444  & 26\\
    OCR-large  & 6173    & 3--14 & chain & 1444  & 26\\
    scene-tree & 1211    & 6     & tree  & 1244  & 2\\
    scene-full & 1211    & 6     & loopy & 1284  & 2\\
    yeast-tree & 1500    & 14    & tree  & 1494  & 2\\
    yeast-full & 1500    & 14    & loopy & 1806  & 2\\
    snake      & 200     &84--168& loopy & 22275 & 11\\
    MSRC21     & 276     & 7--113& loopy &       & 21\\
    Pascal VOC & 964     & 8--112& loopy &       & 21\\
    \bottomrule
